\tool: Revisiting BadUSB with Type-C

### 2021-03-22 WOOT/Files/experiment.tex
screen mirror

		During our experiment, we noticed that some devices did not mirror their screens to our \tool by default. In this case, \tool would inject a sequence of keystrokes to set the victim's device into mirror their screens. In both Windows 10 and Ubuntu (Gnome Desktop), \tool can inject `Win+P' (`Super' is another name for the `Win' key) to switch between different modes for external display. Figure~\ref{fig:ubuntu_switch} illustrates how these keystrokes works on Ubuntu and Windows 10 is similar. In MacOS, according to the official manual~\cite{appleman}, \tool can inject \mbox{`Command+F1'} keystrokes to set the monitor into mirroring the primary screen. In EMUI, there is a special mode called `Desktop Mode', which allows users to use their smartphones like a desktop computer with an external screen. If this mode is victim's default setting, \tool can inject mouse movements to switch to mirror mode as \tool can obtain victim's `desktop' in this mode.

@@

		In our experiment, we found that some devices will notify the user the presence of an external screen. During our experiment, the following notifications were raised:

>>>>

		During our experiment, we noticed that some devices did not mirror their screens to our \tool by default. In this case, \tool would inject a sequence of keystrokes to set the victim's device to mirror the primary screen. In both Windows 10 and Ubuntu (Gnome Desktop), \tool can inject ``Win+P'' (The ``Win'' key is the ``Super'' key in Windows and Ubuntu by default) to switch between different modes for external display. Figure~\ref{fig:ubuntu_switch} illustrates how these keystrokes works on Ubuntu and Windows 10 is similar. In MacOS, according to the official manual~\cite{appleman}, \tool can inject \mbox{``Command+F1''} keystrokes to set the victim's device to mirror the primary screen. In EMUI, there is a special mode called ``Desktop Mode'', which allows users to use their smartphones like a desktop computer with an external screen. If this mode is enabled, as victim's ``desktop'' can be obtained, \tool can inject mouse movements to switch to mirror mode.

@@

		In our experiment, we found that some devices would notify the user the presence of an external screen. During our experiment, the following notifications were raised:
